---
title: "Project Directory Setup"
author: "Joseph J Ferrare"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = TRUE,
  message = TRUE
)
```

## Overview

This document initializes the directory structure and metadata files for the school choice policy discourse analysis project. The current focus is on the pilot phase analyzing Utah legislative committee meetings, while maintaining an expandable structure for additional data sources.

## Load Required Packages

```{r packages}
library(tidyverse)
library(fs)
library(here)
library(glue)

# Source project configuration
source(here("setup", "config.R"))
```

## Create Project Structure

First, verify and create the project directories:

```{r create_structure}
# Function to create and verify directories
setup_project_structure <- function() {
  # Create all directories from config
  walk(unlist(CONFIG$project$dirs), ~dir_create(.x))
  
  # Create data source directories for each state
  for (source in names(CONFIG$project$data_sources)) {
    for (state in CONFIG$project$states$pilot) {  # Just pilot state for now
      source_dirs <- unlist(CONFIG$project$data_sources[[source]])
      walk(source_dirs, ~dir_create(path(.x, state)))
    }
  }
  
  # Return all created paths for verification
  list(
    core_dirs = unlist(CONFIG$project$dirs),
    source_dirs = unlist(CONFIG$project$data_sources)
  )
}

# Create directories and display results
created_dirs <- setup_project_structure()
```

## Initialize Metadata Files

Create metadata tracking files for the pilot phase:

```{r create_metadata}
# Function to initialize metadata files
initialize_metadata_files <- function() {
  # Create legislative meetings index
  legislative_index <- tibble(
    !!!map(CONFIG$metadata$legislative_cols, ~vector(mode = .x, length = 0))
  )
  
  # Create download tracking log
  download_log <- tibble(
    meeting_id = character(),
    state = character(),
    attempt_timestamp = as.POSIXct(character()),
    status = character(),
    error_message = character(),
    download_duration_seconds = numeric(),
    file_hash = character(),
    file_path = character()
  )
  
  # Save files
  write_csv(
    legislative_index,
    path(CONFIG$project$dirs$metadata, "legislative_meetings.csv")
  )
  
  write_csv(
    download_log,
    path(CONFIG$project$dirs$metadata, "download_log.csv")
  )
  
  # Return file paths for verification
  list(
    legislative = path(CONFIG$project$dirs$metadata, "legislative_meetings.csv"),
    download_log = path(CONFIG$project$dirs$metadata, "download_log.csv")
  )
}

# Create metadata files
metadata_files <- initialize_metadata_files()
```

## Validate Setup

Check that everything was created correctly:

```{r validate}
# Function to validate the setup
validate_setup <- function() {
  validation_results <- list()
  
  # Check directories
  all_dirs <- c(
    unlist(CONFIG$project$dirs),
    unlist(CONFIG$project$data_sources)
  )
  
  validation_results$directories <- tibble(
    path = all_dirs,
    exists = dir_exists(path),
    is_directory = is_dir(path)
  )
  
  # Check metadata files
  metadata_files <- c(
    "legislative_meetings.csv",
    "download_log.csv"
  )
  
  validation_results$metadata <- tibble(
    file = metadata_files,
    path = path(CONFIG$project$dirs$metadata, file),
    exists = file_exists(path)
  )
  
  validation_results
}

# Run validation
validation <- validate_setup()

# Display results
cat("\nDirectory Validation:\n")
print(validation$directories)

cat("\nMetadata File Validation:\n")
print(validation$metadata)
```

## Test File Naming Convention

Verify the file naming convention works as expected:

```{r test_naming}
# Create example meeting data
example_meeting <- list(
  state = CONFIG$utah$state$abbreviation,
  date = Sys.Date(),
  chamber = CONFIG$utah$state$chamber,
  committee_abbrev = CONFIG$utah$state$committee$abbreviation,
  meeting_id = 1
)

# Generate test filename
test_filename <- glue(
  CONFIG$filename$legislative$pattern,
  state = example_meeting$state,
  year = format(example_meeting$date, "%Y"),
  month = format(example_meeting$date, "%m"),
  day = format(example_meeting$date, "%d"),
  chamber = example_meeting$chamber,
  committee = example_meeting$committee_abbrev,
  id = str_pad(
    example_meeting$meeting_id, 
    width = CONFIG$filename$legislative$padding$id, 
    pad = "0"
  )
)

cat("\nExample filename:", test_filename, "\n")
```

## Display Project Structure

Show the complete project structure:

```{r show_structure}
# Function to display directory structure
print_dir_structure <- function(path, prefix = "") {
  # List contents
  contents <- dir_ls(path)
  
  # Process each item
  for (item in contents) {
    # Skip certain files/directories
    if (basename(item) %in% c(".git", ".Rproj.user", ".Rhistory")) {
      next
    }
    
    # Print item
    cat(prefix, "├── ", basename(item), 
        if (dir_exists(item)) "/" else "", "\n", sep = "")
    
    # Recurse if directory
    if (dir_exists(item)) {
      print_dir_structure(item, paste0(prefix, "│   "))
    }
  }
}

cat("Project Structure:\n")
print_dir_structure(here())
```

## Session Information

```{r session_info}
sessionInfo()
```